% Code



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```


# Network model

Let's fit an arm-based model using the `rma.mv` function of metafor to get the estimates for each treatment.


```{r}
library(tidyverse)
wm_inc <- read_csv("data/dat-inc.csv")


# create the log of the inc variable
wm_inc <- wm_inc %>%
  mutate(log_inc = log(mean_inc))

# create the sampling variance for the log of inc
wm_inc$vi <- with(wm_inc, (mean_inc_sd^2) / (4 * mean_inc^2))
```

## covariance structure

Now we will fit models with CS, HCS and UN matrix-covariance structure. We will then compare them with `anova` function to choose among the best model.

```{r}

library(metafor)


mv_inc_HCS <- rma.mv(log_inc, vi,
  mods = ~fungicide2,
  random = list(~fungicide2 | factor(study)),
  struct = "HCS",
  method = "ML",
  data = wm_inc
)

mv_inc <- rma.mv(log_inc, vi,
  mods = ~fungicide2,
  random = list(~fungicide2 | factor(study)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = wm_inc
)

mv_inc
```


We can see below that the UN structure is a better model.

```{r}

anova(mv_inc_HCS, mv_inc)
AIC(mv_inc_HCS)
```


## Percent control

Let's obtain the percent control from the estimated ratios.

```{r}

efficacy_inc <- data.frame(cbind(
  (1 - exp(mv_inc$b)) * 100,
  (1 - exp(mv_inc$ci.lb)) * 100,
  (1 - exp(mv_inc$ci.ub)) * 100
))



efficacy_inc
```

## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_inc, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1)
))
```


## Inconsistency 

In a network meta-analysis, it is important to check whether the results are consistent across the different designs. We included this variable manually in the original dataset and tested the interaction effect of treatments and design group.

```{r}

mv_inc_incon <- rma.mv(log_inc, vi,
  mods = ~fungicide2 * design_inc,
  random = list(~factor(study) | design_inc / fungicide2),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = wm_inc
)

anova(mv_inc_incon, btt = 9:13)

anova(mv_inc, mv_inc_incon)
```


## Network Graph



First we  will rename the treatments with the number of trials (within parenthesis) that each treatment was present.

```{r message=FALSE, warning=FALSE}
Sys.setlocale("LC_ALL", "pt_BR.UTF-8") # set UT-8 for displaying names correctly
library(tidyverse)
library(readr)
wm_inc <- read_csv("data/dat-inc.csv")

# Renaming the treatments for the network graph
library(plyr)
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("AACHECK-0" = "CHECK (74)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("DIMO+BOSC-2" = "DIMO+BOSC (72)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("FLUO-2" = "FLUO (73)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("FLUZ-2" = "FLUZ (74)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("PROCY-2" = "PROC (74)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("TIOF-4" = "TIOF (62)"))
wm_inc$fungicide2 <- revalue(wm_inc$fungicide2, c("CARB+PROCY-2" = "CARB+PROC (27)"))
detach("package:plyr", unload = TRUE)
```


Now We need to prepare the data to get the network graph. Thus, we used the package `netmeta` with the function `pairwise` to calculate the contrasts.


```{r message=FALSE, warning=FALSE}
library(netmeta)
pair_inc <- pairwise(
  treat = factor(fungicide2),
  n = 4,
  mean = mean_inc,
  sd = mean_inc_sd,
  studlab = study,
  data = wm_inc,
  sm = "ROM"
)
```

```{r}
net_inc <- netmeta(TE, seTE, treat1, treat2, studlab, data = pair_inc, sm = "ROM", backtransf = TRUE)
summary(net_inc)
```


A network graph is composed of nodes (fungicide treatments) and edges or links between two treatments directly compared in a same trial. This graph allows to visualize how the treatments relate to each other and the number of direct comparisons can be depicted by the thickness of the edges, but also with numbers presented at the top of the links. 

```{r}


netgraph(net_inc,
  plastic = FALSE,
  col = "gray",
  thickness = "number.of.studies",
  points = TRUE,
  col.points = "black",
  cex.points = c("CARB+PROC (27)" = 2.5, "CHECK (74)" = 6, "DIMO+BOSC (72)" = 5.75, "FLUO (73)" = 5.83, "FLUZ (74)" = 6, "PROC (74)" = 6, "TIOF (62)" = 5),
  number.of.studies = TRUE,
  cex.number.of.studies = 1.25,
  col.number.of.studies = "black",
  bg.number.of.studies = "white",
  multiarm = FALSE,
  col.multiarm = "gray",
  pos.number.of.studies = 0.60
)
```




