% Plots


```{r}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figures/',
                       warning=FALSE, message=FALSE)
```

Here we show the scripts that produce the publication-ready plots for the article. There is a hidden script ([see the Rmd file](https://github.com/emdelponte/paper-fungicides-whitemold/blob/master/plots.Rmd)) to prepare the data for the plots including variable creation and transformation. 


```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Load packages
library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(knitr)
library(nloptr)
library(minqa)
library(DT)
library(broom)
library(dplyr)
library(gsheet)
```

```{r include=FALSE}
# Load the data and prepare everything for producing the plots
mofo_br <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit?usp=sharing"
)

target <- c("DIMO+BOSC", "FLUZ", "FLUO", "PROCY", "TIOF", "AACHECK", "CARB+PROCY")
mofo1 <- mofo_br %>%
  filter(fungicide %in% target) %>% # nine fungicides
  filter(n_spray %in% c(0, 2, 4))


mofo1
mofo1 <- mofo1 %>%
  mutate(fungicide2 = paste(fungicide, n_spray, sep = "_"))

unique(mofo1$fungicide2)

mofo1 <- mofo1 %>%
  filter(fungicide2 != "TIOF_2", fungicide2 != "CARB+PROCY_4")
unique(mofo1$fungicide2)

mofo1 <- mofo1 %>%
  mutate(
    inc = as.numeric(inc),
    scl = as.numeric(scl),
    yld = as.numeric(yld),
    inc_check = as.numeric(inc_check),
    scl_check = as.numeric(scl_check),
    yld_check = as.numeric(yld_check),
    inc_mean = as.numeric(inc_mean),
    scl_mean = as.numeric(scl_mean),
    yld_mean = as.numeric(yld_mean),
    inc_qmr = as.numeric(inc_qmr),
    scl_qmr = as.numeric(scl_qmr),
    yld_qmr = as.numeric(yld_qmr),
    inc_cv = as.numeric(inc_cv),
    scl_cv = as.numeric(scl_cv),
    yld_cv = as.numeric(yld_cv)
  )

library(plyr)
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("AACHECK_0" = "CHECK"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("DIMO+BOSC_2" = "DIMO+BOSC"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("FLUO_2" = "FLUO"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("FLUZ_2" = "FLUZ"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("PROCY_2" = "PROC"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("TIOF_4" = "TMET"))
mofo1$fungicide2 <- revalue(mofo1$fungicide2, c("CARB+PROCY_2" = "CARB+PROC"))
detach("package:plyr", unload = TRUE)

# log of inc index
mofo1$log_inc <- log(mofo1$inc)


# log of scl index
mofo1$log_scl <- log(mofo1$scl)


# log of yield
mofo1$log_yld <- log(mofo1$yld)

mofo1 <- mofo1 %>%
  mutate(
    inc_class_1 = ifelse(inc_check < 30, "low", "high"),
    elevation_class = ifelse(elevation > median(elevation), "low", "high"),
    inc_check_class = case_when(inc_check < 30 ~ "Low", inc_check >= 30 ~ "High")
  )


# Sampling variance for the log of inc
mofo1$V_inc <- with(mofo1, inc_qmr / (4 * inc^2)) # numero de rep (n)

# Sampling variance for the log of scl
mofo1$V_scl <- with(mofo1, scl_qmr / (4 * scl^2))


# Sampling variance for log of yield
mofo1$V_yld <- with(mofo1, yld_qmr / (4 * yld^2))

# Sampling variance for yield
mofo1$V_yld2 <- mofo1$yld_qmr / 4 # multivariate approach
```

## Fig 1 Map

```{r}
library(maps)
# Get Brazil map info
brazil_map <- map_data("world", "brazil")

# get shape file
library(rgdal)
brazil <- readOGR("data/shape-files-BRA/BRA_adm1.shp", layer = "BRA_adm1")

mapa <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit#gid=1595668142",
  sheetid = "Map"
)
mapa <- mapa %>%
  mutate(
    lon = as.numeric(lon),
    lat = as.numeric(lat),
    inc = as.numeric(inc)
  )

library(ggrepel)
mapa <- ggplot(mapa) +
  geom_polygon(
    data = brazil,
    aes(x = long, y = lat, group = group),
    fill = "NA", colour = "grey50"
  ) +
  geom_jitter(alpha = 1 / 2, data = mapa, aes(
    x = lon, y = lat,
    size = inc,
    colour = NULL
  )) +
  coord_fixed() +
  theme_minimal() +
  theme(legend.position = "top") +
  labs(x = "Longitude", y = "Latitude") +
  scale_size_continuous(name = "Mean incidence untreated plots (%)") +
  geom_label_repel(aes(x = lon, y = lat, size = 7, label = name),
    box.padding = unit(0.3, "lines"),
    point.padding = unit(0.8, "lines"),
    fontface = "bold", segment.size = 0.5, size = 2
  ) +
  coord_map(xlim = -c(60, 40), ylim = -c(34, 10))

mapa
ggsave("Fig1.png", width = 6, height = 6, dpi = 300)
```


## Fig 3 Boxp disease per season

```{r, warning=FALSE}
inc_year <- mofo1 %>%
  filter(fungicide == "AACHECK") %>%
  ggplot(aes(year, inc_check)) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2, color = "gray50") +
  labs(x = "Crop Seasons", y = "Incidence (%)") +
  theme_grey() +
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100), limits = c(0, 100))
inc_year


scl_year <- mofo1 %>%
  filter(fungicide == "AACHECK") %>%
  ggplot(aes(year, scl_check)) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2, color = "gray50") +
  labs(x = "Crop Seasons", y = "Sclerotia Mass (g/ha)") +
  theme_grey() +
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1))
scl_year


library(cowplot)
box_year <- plot_grid(inc_year, scl_year, labels = c("A", "B"), ncol = 2, align = "HV")
box_year

ggsave("Fig3.png", width = 8, height = 4, dpi = 300)
```


## Fig 4 Box disease per fungicide

```{r, message=FALSE, warning=FALSE}
mofo1$fungicide2 <- factor(mofo1$fungicide2, levels = c("CHECK", "CARB+PROC", "DIMO+BOSC", "FLUO", "FLUZ", "PROC", "TMET"))

box_inc <- ggplot(mofo1, aes(fungicide2, inc)) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2, color = "gray50") +
  labs(x = "Fungicide", y = "Incidence (%)") +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100), limits = c(0, 100)) +
  theme_grey() +
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")
```



```{r, message=FALSE, warning=FALSE}
mofo1$fungicide2 <- factor(mofo1$fungicide2, levels = c("CHECK", "CARB+PROC", "DIMO+BOSC", "FLUO", "FLUZ", "PROC", "TMET"))
box_scl <- ggplot(mofo1, aes(fungicide2, scl)) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2, color = "gray50") +
  labs(x = "Fungicide", y = "Sclerotia Mass (g/ha)") +
  theme_grey() +
  # scale_y_continuous(breaks=c(0,  5000, 10000), limits=c(0,10000))+
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")


library(cowplot)
box_inc_scl <- plot_grid(box_inc, box_scl, labels = c("A", "B"), ncol = 2, align = "HV")
box_inc_scl

ggsave("Fig4.png", width = 9, height = 4, dpi = 300)
```



## Fig 5 Scatter disease variables

```{r}
library(ggrepel)
scl_inc <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit#gid=41911812",
  sheetid = "inc_scl"
)
scl_inc <- scl_inc %>%
  mutate(
    inc = as.numeric(inc),
    scl = as.numeric(scl),
    inc_inf = as.numeric(inc_inf),
    inc_sup = as.numeric(inc_sup),
    scl_inf = as.numeric(scl_inf),
    scl_sup = as.numeric(scl_sup)
  )

library(plyr)
scl_inc$Fungicide <- revalue(scl_inc$Fungicide, c("TIOF" = "TMET"))
detach("package:plyr", unload = TRUE)

set.seed(42)
ggplot(scl_inc, aes(inc, scl)) +
  geom_smooth(colour = "black", method = "lm") +
  geom_errorbar(aes(ymin = scl_inf, ymax = scl_sup), width = 0.2, size = 0.5, color = "gray45") +
  geom_errorbarh(aes(xmin = inc_inf, xmax = inc_sup), height = 0.5, size = 0.5, color = "gray45") +
  ylab("Sclerotia mass reduction (%)") +
  xlab("White mold incidence reduction (%)") +
  scale_y_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90), limits = c(40, 93)) +
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100), limits = c(40, 93)) +
  geom_label_repel(aes(inc, scl, label = scl_inc$Fungicide),
    fill = "grey90", size = 3, color = "black", label.size = 0.30,
    box.padding = unit(0.30, "lines")
  ) +
  geom_point(aes(inc, scl)) +
  theme_grey(base_size = 16) +
  coord_fixed() +
  theme(legend.position = "none", axis.text = element_text(size = 10), axis.title = element_text(size = 10), panel.background = element_rect(fill = "grey96", color = "grey96"))
ggsave("Fig5.png", width = 5, height = 4, dpi = 300)
```


##  Fig 6 Box yield season and fungicide

```{r, message=FALSE, warning=FALSE}
mofo1$fungicide2 <- factor(mofo1$fungicide2, levels = c("CHECK", "CARB+PROC", "DIMO+BOSC", "FLUO", "FLUZ", "PROC", "TMET"))
box_yld <- ggplot(mofo1, aes(fungicide2, yld)) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2.5, color = "gray50") +
  labs(x = "Fungicide", y = "Yield (kg/ha)") +
  theme_grey() +
  ylim(1000, 5000) +
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

yld_year <- mofo1 %>%
  filter(fungicide == "AACHECK") %>%
  ggplot(aes(year, yld_check)) +
  ylim(1000, 5000) +
  geom_boxplot(size = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.1, shape = 1, size = 2.5, color = "gray50") +
  labs(x = "Crop Seasons", y = "Yield (Kg/ha)") +
  theme_grey() +
  theme(panel.background = element_rect(fill = "grey96", color = "grey96"), axis.text.x = element_text(angle = 45, hjust = 1))

library(cowplot)
yld_box <- plot_grid(yld_year, box_yld, labels = c("A", "B"), nrow = 1, align = "H")
yld_box

ggsave("Fig6.png", width = 9, height = 4, dpi = 300)
```


## Fig 7 Scatter yield x disease


```{r}
library(cowplot)
library(ggrepel)
library(tidyverse)
inc_yld <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit#gid=2054312057",
  sheetid = "inc_yld"
)
inc_yld <- inc_yld %>%
  mutate(
    inc = as.numeric(inc),
    yld = as.numeric(yld),
    inc_inf = as.numeric(inc_inf),
    inc_sup = as.numeric(inc_sup),
    yld_inf = as.numeric(yld_inf),
    yld_sup = as.numeric(yld_sup)
  )

library(plyr)
inc_yld$Fungicide <- revalue(inc_yld$Fungicide, c("TIOF" = "TMET"))
detach("package:plyr", unload = TRUE)

set.seed(42)
gr1 <- ggplot(inc_yld, aes(inc, yld)) +
  geom_smooth(colour = "black", method = "lm") +
  geom_errorbar(aes(ymin = yld_inf, ymax = yld_sup), width = 0.2, size = 0.5, color = "gray45") +
  geom_errorbarh(aes(xmin = inc_inf, xmax = inc_sup), height = 5, size = 0.5, color = "gray45") +
  ylab("Yield difference (kg/ha)") +
  xlab("White mold incidence control (%)") +
  scale_y_continuous(breaks = c(200, 300, 400, 500, 600, 700, 800), limits = c(200, 750)) +
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90), limits = c(40, 90)) +
  geom_label_repel(aes(inc, yld, label = inc_yld$Fungicide),
    fill = "grey90",
    size = 3.5, color = "black", label.size = 0.25,
    box.padding = unit(0.30, "lines")
  ) +
  geom_point(aes(inc, yld)) +
  theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 10), panel.background = element_rect(fill = "grey96", color = "grey96"), axis.title = element_text(size = 12), legend.position = "none")

gr1
```




```{r}
scl_yld <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit#gid=1324985291",
  sheetid = "scl_yld"
)
scl_yld <- scl_yld %>%
  mutate(
    yld = as.numeric(yld),
    scl = as.numeric(scl),
    yld_inf = as.numeric(yld_inf),
    yld_sup = as.numeric(yld_sup),
    scl_inf = as.numeric(scl_inf),
    scl_sup = as.numeric(scl_sup)
  )

library(plyr)
scl_yld$Fungicide <- revalue(scl_yld$Fungicide, c("TIOF" = "TMET"))
detach("package:plyr", unload = TRUE)

set.seed(42)
gr2 <- ggplot(scl_yld, aes(scl, yld)) +
  geom_smooth(colour = "black", method = "lm") +
  geom_errorbarh(aes(xmin = scl_inf, xmax = scl_sup), height = 5, size = 0.5, color = "gray45") +
  geom_errorbar(aes(ymin = yld_inf, ymax = yld_sup), width = 0.2, size = 0.5, color = "gray45") +
  ylab("Yield difference (kg/ha)") +
  xlab("Sclerotia control (%)") +
  scale_y_continuous(breaks = c(200, 300, 400, 500, 600, 700, 800), limits = c(200, 750)) +
  scale_x_continuous(breaks = c(40, 50, 60, 70, 80, 90, 100), limits = c(40, 95)) +
  geom_label_repel(aes(scl, yld, label = scl_yld$Fungicide),
    fill = "grey90", size = 3.5, color = "black", label.size = 0.50,
    box.padding = unit(0.30, "lines")
  ) +
  geom_point(aes(scl, yld)) +
  theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.position = "none", panel.background = element_rect(fill = "grey96", color = "grey96"))
gr2
```


```{r}
library(cowplot)
efficacy_plot <- plot_grid(gr1, gr2, labels = c("A", "B"), ncol = 2, align = "HV")
efficacy_plot

ggsave("Fig7.png", width = 9, height = 5, dpi = 300)
```

## Fig 8 tile risk categories 



```{r}

mofo <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1VLK94nZV9DhYNVEUXFb7aC5BjhJ21FYfLf8crj5m-a8/edit#gid=2085223602",
  sheetid = "Probability"
)
mofo <- mofo %>%
  mutate(
    tau = as.numeric(tau),
    D = as.numeric(D)
  )
library(plyr)
mofo$fungicide <- revalue(mofo$fungicide, c("TIOF" = "TMET"))
detach("package:plyr", unload = TRUE)

prob <- function(C, P, tau, D) {
  profit <- (D - (C / (P / 1000))) / sqrt(tau) # loss
  prob_gain <- pnorm(profit)
  prob_gain
}



for (i in 1:length(mofo$C)) {
  mofo$breacking_even[i] <- prob(C = mofo$C[i], D = mofo$D[i], tau = mofo$tau[i], P = mofo$P[i]) * 100
}



library(viridis)
library(tidyverse)
library(ggthemes)
dat <- mofo %>%
  mutate(
    breacking_even = as.numeric(breacking_even),
    breacking_even = round(breacking_even, 1)
  )


dat %>%
  mutate(breacking_even1 = case_when(
    breacking_even >= 75 ~ "p \u2265 75  ",
    breacking_even < 75 & breacking_even >= 65 ~ "65 \u2265 p < 75  ",
    breacking_even < 65 & breacking_even >= 55 ~ "55 \u2265 p < 65  ",
    breacking_even < 55 & breacking_even >= 45 ~ "45 \u2265 p < 55  ",
    breacking_even < 45 ~ "0 \u2265 p < 45  "
  )) %>%
  ggplot(aes(factor(C), factor(P), z = breacking_even1, fill = breacking_even1, label = breacking_even1)) +
  geom_tile(color = "white", size = 0.5) +
  scale_fill_viridis(discrete = T, option = "D", begin = 0, end = 1, name = "Probability of breaking-even (%)") +
  scale_color_gradient(high = "white", low = "white") +
  labs(x = "Fungicide + application cost (US$/ha)", y = "Soybean price (US$/ton) ", fill = "") +
  # facet_wrap(~fungicide, ncol = 2, scales = "free", dir = "h")+
  theme_minimal() +
  facet_grid(class ~ fungicide, scales = "free") +
  theme(text = element_text(size = 12), legend.justification = "center", strip.text.x = element_text(size = 12, face = "bold"), strip.text.y = element_text(size = 12, face = "bold"), panel.grid.minor = element_line(colour = "white"), panel.grid.major = element_line(colour = "white"), legend.position = "bottom")
ggsave("Fig8.png", width = 8, height = 7, dpi = 300)
```



## Fig 1 Supplement

```{r, warning=FALSE}
## Log of the Effect-sizes
mofo1 <- mofo1 %>%
  mutate(
    log_inc = log(inc),
    log_scl = log(scl),
    log_yld = log(yld)
  )


hist_log_inc <- ggplot(mofo1, aes(log_inc)) + geom_histogram(binwidth = 0.5, color = "black") + xlab("log(Incidence)")


hist_inc <- ggplot(mofo1, aes(inc)) + geom_histogram(binwidth = 6, color = "black") + xlab("Incidence (%)")


hist_log_scl <- ggplot(mofo1, aes(log_scl)) + geom_histogram(binwidth = 0.5, color = "black") + xlab("log(Sclerotia Mass)")


hist_scl <- ggplot(mofo1, aes(scl)) + geom_histogram(binwidth = 1500, color = "black") + xlab("Sclerotia Mass (g/ha)")


hist_log_yld <- ggplot(mofo1, aes(log_yld)) + geom_histogram(binwidth = 0.06, color = "black") + xlab("log(Yield)")


hist_yld <- ggplot(mofo1, aes(yld)) + geom_histogram(binwidth = 200, color = "black") + xlab("Yield (Kg/ha)")


library(cowplot)
hist_plot <- plot_grid(hist_inc, hist_log_inc, hist_scl, hist_log_scl, hist_yld, labels = c("A", "D", "B", "E", "C"), nrow = 3, align = "V")
hist_plot


ggsave("Fig1_supp.png", width = 8, height = 11, dpi = 300)
```



